msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-10 paper.tex
Added blurb about trapped recombinations.

In human-like parameter regimes, \msprime's implementation of the
exact coalescent with recombination comprehensively outperforms
all other simulators, including those based on SMC
approximations~\citep{kelleher2016efficient}. However, it is important
to note that although the implementation of Hudson's algorithm is
very efficient, it is still quadratic in the scaled recombination rate
$\rho$, and therefore for sufficiently large $N_e$, recombination rate
or long genome, efficient SMC implementations will be faster
that \msprime.

>>>>

In human-like parameter regimes, \msprime's implementation of the
exact coalescent with recombination comprehensively outperforms
all other simulators, including those based on SMC
approximations~\citep{kelleher2016efficient}. However, it is important
to note that although the implementation of Hudson's algorithm is
very efficient, it is still quadratic in the scaled recombination rate
$\rho. This is because Hudson's algorithms tracks recombinations not only 
in segments ancestral to the sample, but also between ancestral segments.     
Estimates of the number of such "trapped" recombinations grow quadratically 
with genome length (\cite{Hein, Schierup, Wiuf}, Eq. 5.10). 
Because they do not track such recombinations, efficient SMC implementations 
will be faster that \msprime for sufficiently high recombination rate, 
genome length, or $N_e$. %Until we decide to approximate the recombination process
%between distant ancestral segment. Hint hint.
